---
title: "Assignment 1"
author: "Kowsick Ram"
date: "2022-09-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. What happens if you make a scatterplot of class vs drv. Why is the plot not useful?

Ans:The class and drv attributes are categorical. Therefore the plot shows the mapping between these categories.
```{r}
ggplot(data = mpg) + 
  geom_point(mapping = aes(x = class, y = drv))
```
2.What’s gone wrong with this code? Why are the points not blue?
```{r}
ggplot(data = mpg) + 
geom_point(mapping = aes(x = displ, y = hwy), color = "blue")
```
Ans:The points are not blue, because the color layer is specified within the aes mappings. Thus the framework tries to plot the color against an attribute “blue”, but this does not exist within the data. The correct code would be to set the color manually in the geom_point method.


3.A.What happens if you map a aesthetic to something other than a variable name, like aes(colour = displ < 5)?            

Ans:
```{r}
ggplot(data = mpg) + geom_point(mapping = aes(x = displ, y = hwy, colour = displ < 5))

```


B.What does the stroke aesthetic do? What shapes does it work with?

Ans:The stroke aesthetic seems to adjust the plotted object thickness.

4 Read ?facet_wrap. What does nrow do? What does ncol do? What other options control the layout of the individual panels? Why doesn’t facet_grid() have nrow and ncol variables?

Ans:Facet grids do not have these configuration because the rows and cols are determined by the specified attributes.

?facet_wrap

 5
a) What plots does the following code make? What does . do?

```{r}
ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy)) +
facet_grid(drv ~ .)

ggplot(data = mpg) +
geom_point(mapping = aes(x = displ, y = hwy)) +
facet_grid(. ~ cyl)
```


b) When using facet_grid() you should usually put the variable with more unique
levels in the columns. Why?

Answer: 
    facet_grid divides the plot in the particular area. That used to make plot into subplot. it gives the meaningful graph.


6)What geom would you use to draw a line chart? A boxplot? A histogram? An area chart?
Ans:line chart: geom_line()
boxplot chart: geom_boxplot();
  area chart: geom_area();
  
```{r}
ggplot(data=mpg)+
  geom_line(aes(x=displ,y=hwy))
ggplot(data=mpg)+
  geom_boxplot(aes(x=displ,y=hwy))
ggplot(data=mpg)+
  geom_area(aes(x=displ,y=hwy))

```


7)Will these two graphs look different? Why/why not?
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) + 
     geom_point() +
     geom_smooth()
ggplot() +
     geom_point(data = mpg, mapping = aes(x = displ, y = hwy)) +
     geom_smooth(data = mpg, mapping = aes(x = displ, y = hwy))
Ans:No, the two graphs looks similar.  Because both geom_point() and geom_smooth() use same data and mappings.
     



8)What does geom_col() do? How is different to geom_bar()?
Ans:
```{r}
ggplot(data=mpg)+
  geom_bar(mapping=aes(x=class))
```
```{r}
ggplot(data=mpg)+
  geom_col(mapping=aes(x=displ,y=hwy))
```
Answer: 
  barchart 
  requires only x whereas column chart requires both x and y

9)What is the default geom associated with stat_summary()? How could you rewrite the previous plot to use that geom function instead of the stat function?
Ans:

The default geom associated with stat_summary is geom_pointrange.
```{r}
ggplot(data=mpg)+
  geom_pointrange(aes(x=displ,y=hwy),
                  stat="summary",
             fun.ymin=min,
             fun.ymax=max,
             fun=median)

```



10)What does the plot below tell you about the relationship between city and highway mpg? Why is coord_fixed() important? What does geom_abline() do?
ggplot(data = mpg, mapping =aes(x =cty, y =hwy)) +
geom_point() +
geom_abline() +
coord_fixed()
Ans:
City milage increases when the highway milage increases 
There is a positive relation between city and highway.
    coord_fixed(): adjust the value in the data set
    geom_abline():it show the prediction between x and y. It shows regression line

